Air cargo load and route planning in pickup and delivery operations

### 2024-01-28 latex/eswa.tex
Main flow description added

{\color{blue}
Scenario 6 will be used only for the best method validation.

Figure \ref{fig:flow} depicts the Algorithm \ref{alg:main} for easy understanding of the main flow.

@@

		%% Make the boxes
		\node [mybox] (first)                        {Select:\\ 1. scenario\\2. surplus\\3. time limit};
		\node [mybox, right=0.7cm of first] (second) {Config:\\4. parameters\\5. cost matrix\\6. pallets\\7. items};
		\node [mybox, right=0.7cm of second] (third) {8. Define tour\\     schema:\\- All tours\\ \ \ \ (K-1)!\\ \ \ \ or\\- Solve a TSP\\ \ \ \ (set of tours))};
		\node [mybox, right=0.7cm of third] (fourth) {Solve ACLPP+RPDP:\\9. Many tours\\ \ \ \ (node-by-node)\\10. Select best tour};

@@

>>>>

{\color{blue}
Scenario 6 will be used only for the best method validation.
}

@@

		%% Make the boxes
		\node [mybox] (first)                        { \small {\bf Select:}\\ \small 1. scenario\\ \small 2. surplus\\ \small 3. time limit};
		\node [mybox, right=0.7cm of first] (second) { \small {\bf Config:}\\ \small 4. parameters\\ \small 5. cost matrix\\ \small 6. pallets\\ \small 7. items};
		\node [mybox, right=0.7cm of second] (third) { \small 8. {\bf Define tour}\\  \small      schema:\\ \small - All tours\\ \ \ \ (K-1)!\\ \ \ \  \small or\\ \small - Solve a TSP\\ \small  \ \ \ (set of tours))};
		\node [mybox, right=0.7cm of third] (fourth) { \small {\bf Solve ACLPP+RPDP:}\\ \small 9. Many tours\\ \small  \ \ \ (node-by-node)\\ \small 10. Select best tour};

@@

{\color{blue}
Figure \ref{fig:flow} depicts the Algorithm \ref{alg:main} for easy understanding of the main flow. (1.) Select a scenario from Table \ref{tab:scenarios}. (2.) Select a volume surplus (1.2, 1.5, or 2.0). (3.) Establish a time limit (240s, 1200s, 2400s, or 3600s). (4.) Configure the parameters presented in the mathematical formulation. (5.) Load the distance matrix and calculate the matrix cost according to the aircraft characteristics. (6.) Load the pallet configuration parameters. (7.) Load the item instance (all items to be transported) into memory. (8.) Choose a tour schema. Until 7 nodes, it is practical to generate (K-1)! tours. For a larger number of nodes, we recommend using a TSP heuristic that generates a set of similar suboptimal tours. (9.) and (10.) solve all tours and select the best.
}
